Changelog

### 2021-05-24 Chapter-5/Chapter-5.tex
Updates from Overleaf

This paper makes the following contributions:

@@

\section{Background and Threat Model}
In the section, we give an overview of the background knowledge of information theory and present the threat model of the paper.

@@

In the paper, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as

@@

We consider an attacker who shares the same hardware resource with the victim. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the paper. This is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Also, like recent works, we assume the attacker has a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible key ($k \in K$). The program also takes known messages $M$ as the input.

@@

In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

@@

According to Chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. In this paper, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent. We use the above method to test if any two leakage sites are independent for each leakage point. We combine them into a leakage are calculate the total amount of the leakage.
\section{Design}
In this section, we explain the implementation of \ctool{}.
We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

@@

\subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $. In the paper, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.

>>>>

This chapter makes the following contributions:

@@

\section{Background and Threat Model}
In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.

@@

In the chapter, we use the channel capacity to describe the amount of information leakages through a channel. In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel. If we use $K$ to represent the input secrets and $O$ to represent the output observation. The channel capacity ($C$) is defined as

@@

We consider an attacker who shares the same hardware resource with the victim. The attacker may not know the memory access the victim program accesses directly. Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program. We call the memory access information as the observation ($O$) in the rest of the chapter. This is a typical scenario for most side-channel attacks.  We also assume the attacker can have access to the source code of the victim program ($\beta$). It is a valid assumption since most side-channel attacks target open-source software. Also, like recent works, we assume the attacker has a noise-free observation. For some side-channel channels like the controlled-channel attacks, it is already true. The program ($\beta$) has $K$ as the sensitive input. $K$ is a finite set that consists of every possible key ($k \in K$). The program also takes known messages $M$ as the input.

@@

In thios chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

@@

According to Chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. In thios chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent. We use the above method to test if any two leakage sites are independent for each leakage point. We combine them into a leakage are calculate the total amount of the leakage.
\section{Design}
In this section, we explain the implementation of \ctool{}.
We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

@@

\subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $. In the chapter, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.

### 2021-05-24 changelog.tex
Updates from Overleaf

I have a few choices to address the limitations. First, I can use static analysis (model checking or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are several papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

@@

Like many other research projects,

>>>>

I have a few choices to address the limitation. First, I can use static analysis (model checking or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are several papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

@@

Like many other research projects, the research presented in the dissertation has a few limitations.

a. It is true that the methods in the dissertation can not find all kinds of side-channel leakages. No tool can find all forms of leakages. Even for address-based side-channel leakages, Abacus
